Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-12 research_class/paper.tex
Add missing indefinite article.

These new browser capabilities also bring with them the traditional
challenges of building reliable distributed applications, such as:
concurrency, security, scalability, naming, discovery, replication,
relocation, etc. The solutions to many of these challenges involve
the proper management of distributed state. Distributed consensus is
one category of distributed state management in which multiple nodes
must come to agreement on the state of single value or set of values. % TODO/CITE
The grandparent of distributed consensus algorithms is the Paxos
algorithm described by Leslie Lamport \cite{paxos:lamport98}. However,
Paxos has been notoriously difficult to understand and to implement
correctly \cite{paxos:chandra07}. Raft is a more recent distributed
consensus algorithm that aims for understandability and practicality
of implementation \cite{raft_thesis:ongaro14}.

>>>>

These new browser capabilities also bring with them the traditional
challenges of building reliable distributed applications, such as:
concurrency, security, scalability, naming, discovery, replication,
relocation, etc. The solutions to many of these challenges involve
the proper management of distributed state. Distributed consensus is
one category of distributed state management in which multiple nodes
must come to agreement on the state of a single value or set of values. % TODO/CITE
The grandparent of distributed consensus algorithms is the Paxos
algorithm described by Leslie Lamport \cite{paxos:lamport98}. However,
Paxos has been notoriously difficult to understand and to implement
correctly \cite{paxos:chandra07}. Raft is a more recent distributed
consensus algorithm that aims for understandability and practicality
of implementation \cite{raft_thesis:ongaro14}.
